An efficient acyclic contact planner for multiped robots

### 2017-01-16 body/contact.tex
updates
Jospeh s comments

% !TEX root =  ../main.tex
\section{From a guide path to a discrete sequence of contact configurations ($\mathcal{P}_2$)}
\label{sec:contact}
In the second phase, we compute a discrete sequence of static equilibrium configurations $\mathbf{Q}^{\overline{0}}$ given a root path
$\mathbf{q}^0(t) : [0,1] \longrightarrow$ \gls{$C_{Reach}^0 \simeq C_{Equil}^0$}. This contact planner is built on top of
a contact generator, used to generate static equilibrium configurations. We first describe the generator, before detailing the contact planning algorithm.
%~ Our planner computes guide paths in $C_{Reach}^0$ , an approximation of \gls{$C_{Equil}^0$}.
%~ As an input of this stage, we however assume an \gls{equilibrium feasible} root guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow$ \gls{$C_{Equil}^0$}.
%~ If this is not the case, our planner will fail rapidly, thus allowing replanning, as discussed in Section~\ref{sec:perf}.
%~ We now consider the second problem of computing a discrete sequence of equilibrium configurations $\mathbf{Q}^{\overline{0}}$ along $\mathbf{q}^0(t)$.

@@

\begin{figure*}
  \centering
  \begin{overpic}[width=0.8\linewidth]{figures/contact_gen}
		\put (1,1) {a} 
		\put (22,1) {b} 
		\put (42,1) {c} 
		\put (62,1) {d} 
		\put (83,1) {e} 
	\end{overpic}
  \caption{Generation of a contact configuration for the right leg of HRP-2. (a): Selection of reachable obstacles. (b): Entries of the limb samples database (with $N = 4$). (c): With a proximity query on the octree database, configurations too far from obstacles are eliminated. (d): The best candidate according to a user-defined heuristic $h$ is chosen. (e): The final contact is achieved using inverse kinematics.}
  \label{fig:contact_gen}
\end{figure*}

@@

%\subsection{Generation of a contact configuration}  
\subsubsection{Creating contacts:}
Contacts are created using a FIFO approach: we try first to create a contact with the limb that has been contact-free the longest. If the contact creation was not successful, the limb is pushed on top of the queue, and will only be tried again after the others.
%~ \begin{enumerate}
%~ \item \deladp{At most one contact creation happens between two consecutive steps. }
%~ \item \deladp{A contact is validated if and only if the resulting configuration is in static equilibrium;}
%~ \item \deladp{We use a FIFO approach:  we always try first to create a contact with the limb that has been contact-free the longest. If the contact creation
%~ was not successful for a limb, the limb is pushed on top of the queue, and will only be tried again after the others.}
%~ \end{enumerate}

>>>>

% !TEX root =  ../main.tex
\section{From a guide path to a discrete sequence of contact configurations ($\mathcal{P}_2$)}
\label{sec:contact}
In the second phase, we compute a discrete sequence of static equilibrium configurations $\mathbf{Q}^{\overline{0}}$ given a root path
$\mathbf{q}^0(t) : [0,1] \longrightarrow$ \gls{$C_{Reach}^0$}. This contact planner is built on top of
a contact generator, used to generate static equilibrium configurations. We first describe the generator, before detailing the contact planning algorithm.
%~ Our planner computes guide paths in $C_{Reach}^0$ , an approximation of \gls{$C_{Equil}^0$}.
%~ As an input of this stage, we however assume an \gls{equilibrium feasible} root guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow$ \gls{$C_{Equil}^0$}.
%~ If this is not the case, our planner will fail rapidly, thus allowing replanning, as discussed in Section~\ref{sec:perf}.
%~ We now consider the second problem of computing a discrete sequence of equilibrium configurations $\mathbf{Q}^{\overline{0}}$ along $\mathbf{q}^0(t)$.

@@

\begin{figure*}
  \centering
  \begin{overpic}[width=0.8\linewidth]{figures/contact_gen}
		\put (1,1) {a} 
		\put (22,1) {b} 
		\put (42,1) {c} 
		\put (62,1) {d} 
		\put (83,1) {e} 
	\end{overpic}
  \caption{Generation of a contact configuration for the right leg of HRP-2. (a): Selection of reachable obstacles. (b): Entries of the limb samples database (with $N = 4$). (c): With a proximity query between the octree database and the obstacles, configurations too far from obstacles are discarded. (d): The best candidate according to a user-defined heuristic $h$ is chosen. (e): The final contact is achieved using inverse kinematics.}
  \label{fig:contact_gen}
\end{figure*}

@@

%\subsection{Generation of a contact configuration}  
\subsubsection{Creating contacts:}
Contacts are created using a FIFO approach: we try first to create a contact with the limb that has been contact-free the longest. If the contact creation does not succeeds, the limb is pushed on top of the queue, and will only be tried again after the others.
%~ \begin{enumerate}
%~ \item \deladp{At most one contact creation happens between two consecutive steps. }
%~ \item \deladp{A contact is validated if and only if the resulting configuration is in static equilibrium;}
%~ \item \deladp{We use a FIFO approach:  we always try first to create a contact with the limb that has been contact-free the longest. If the contact creation
%~ was not successful for a limb, the limb is pushed on top of the queue, and will only be tried again after the others.}
%~ \end{enumerate}

### 2017-01-16 body/overview.tex
Jospeh s comments

%\subsubsection{Environment and other volumes} 
%\label{sec:A}
\medskip
\noindent $W^0$ is a volume encompassing $R^0$ (Figure~\ref{fig:HyQ_roms}). \\
 %~ (Figure~\ref{fig:character}-right: central cylinder). 
 $W^k$ is the reachable workspace of a limb $R^k$: %(Figure~\ref{fig:character}-right: the four ellipses). 
\begin{equation}
  W^k = \left\{ {\mathbf{x} \in \mathbb{R}^3: \exists \, \mathbf{q}^k \in C^k_{jl}, \mathbf{p}^k(\mathbf{q}^k) = \mathbf{x} } \right\}
\end{equation}
%~ \adnote{in this definition you don't account for joint limits}
where $\mathbf{p}^k$ denotes the end-effector position of $R^k$ (translation only) for $\mathbf{q}^0 = \mathbf{0}$ being the null displacement, and  $C^k_{jl}$ is the space
of admissible limb joint configurations. We also define \mbox{$W = \bigcup_{k=1}^{l}W^k$}, and
$W^k(\mathbf{q}^{0})$ (for $1 \leq k \leq l$) as the volume $W^k$ for the root configuration $\mathbf{q}^{0}$.

>>>>

%\subsubsection{Environment and other volumes} 
%\label{sec:A}
\medskip
\noindent $W^0$ is a volume encompassing $R^0$ (Figure~\ref{fig:HyQ_roms}). \\
 %~ (Figure~\ref{fig:character}-right: central cylinder). 
 $W^k$ is the reachable workspace of a limb $R^k$: %(Figure~\ref{fig:character}-right: the four ellipses). 
\begin{equation}
  W^k = \left\{ {\mathbf{x} \in \mathbb{R}^3: \exists \, \mathbf{q}^k \in C^k_{j.lim}, \mathbf{p}^k(\mathbf{q}^k) = \mathbf{x} } \right\}
\end{equation}
%~ \adnote{in this definition you don't account for joint limits}
where $\mathbf{p}^k$ denotes the end-effector position of $R^k$ (translation only) for $\mathbf{q}^0 = \mathbf{0}$ being the null displacement, and  $C^k_{j.lim}$ is the space
of admissible limb joint configurations. We also define \mbox{$W = \bigcup_{k=1}^{l}W^k$}, and
$W^k(\mathbf{q}^{0})$ (for $1 \leq k \leq l$) as the volume $W^k$ for the root configuration $\mathbf{q}^{0}$.

### 2017-01-16 body/rbprm.tex
Jospeh s comments

\subsection{The compromising reachability condition}
\label{sec:scaling}
The ideal shape $B^*, W^0 \subset B* \subset B^{\textrm{\it Suf}}$ that defines a necessary \textbf{and} sufficient condition for contact creation has no analytical definition.
Therefore, we approximate $B^*$ to define the contact reachable space $C_{Reach}^0$.

>>>>

\subsection{The compromising reachability condition}
\label{sec:scaling}
The ideal shape $B^*, W^0 \subset B* \subset B^{\textrm{\it Suf}}$ that defines a necessary \textbf{and} sufficient condition for contact creation has no explicit definition.
Therefore, we approximate $B^*$ to define the contact reachable space $C_{Reach}^0$.
